Commutative character sheaves and geometric types for supercuspidal representations

### 2020-08-07 Geometric types.tex
Added H1b examples

@@

@@

>>>>

We give examples illustrating Hypothesis \ref{H1b}: first,
an example of a quasicharacter that does not vanish on $G_{i, \der}(k)$,
and then a class of Yu data where it is always satisfied.
Let $G = \SL_2$ over $\QQ_2$.
Then the hyperspecial maximal compact $\oK^0$ reduces to $\SL_2(\ZZ/2^{d+1}\ZZ)$ at depth $d$.
The derived subgroup of $\SL_2(\ZZ/2\ZZ)$ has index $2$, while it has index $4$ in positive depth.
There is therefore a character $\varphi^0$ of $K$ of order $4$ and depth $1$
factoring through the quotient of $\SL_2(\ZZ/4\ZZ)$ by its derived subgroup.
Taking the trivial representation for $\orho^0$ gives a Yu datum not satisfying \ref{H1b}. \todo{Does Yu require tameness?  Can we say that this is an example if so?}

In contrast, there is a broad class of representations that automatically satisfy \ref{H1b}.
Recall that a representation is \emph{toral} \citelist{\cite{adler:98a} \cite{kaletha:19a}*{\S 6}}
if it arises from a Yu datum of the form $(S \subset G, \orho^0=1, (\varphi^{d-1}, 1)$ where
$S$ is an elliptic maximal torus and $\varphi^{d-1}$ is $G$-generic character of $S(F)$ of positive depth.
Since $S$ is abelian, it has trivial derived subgroup and thus \ref{H1b} is satisfied.
Toral representations include epipelagic representations \cite{reeder-yu:14a} and
the representations considered by Reeder in \cite{reeder:08a}.

@@

\bib{adler:98a}{article}{
	author={Adler, Jeffrey},
	title={Refined  anisotropic $K$-types  and  supercuspidal  representations},
	journal={Pacific J. Math.},
	volume={185},
	date={1998},
	number={1},
	pages={1--32},
}

@@

\bib{reeder:08a}{article}{
    author={Reeder, Mark},
    title={Supercuspidal $L$-packets of positive depth and twisted {Coxeter} elements},
    journal={J. Reine Angew. Math.},
    volume={620},
    date={2008},
    pages={1--33},
}

\bib{reeder-yu:14a}{article}{
    author={Reeder, Mark},
    author={Yu, Jiu-Kang},
    title={Epipelagic representations and invariant theory},
    journal={J. Amer. Math. Soc.},
    volume={27},
    number={2},
    pages={437--477},
}
